Parameterized convection, stratiform clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-09-11 resolution.tex
edits

To isolate the relative importance of temperature or moisture on the systematic reduction in dilute CAPE with resolution for both ascending/descending regimes, dilute CAPE is recomputed for all resolutions, but through fixing the moisture profiles to the lowest resolution $ne20$ profile, and then through fixing only the temperature to the $ne20$ profile. Figure~\ref{fig:cape}d shows the influence of changing temperature profile with resolution on dilute CAPE of ascending/descending grid columns, and illustrates that the systematic reduction in dilute CAPE with resolution in both regimes is primarily from changes to the temperature field. Moisture changes with resolution has a smaller influence, only appreciably impacting the dilute CAPE of ascending regions at higher resolutions (not shown).

@@

This study argues that the sensitivity of parameterized convection and stratiform precipitation rates to resolution are a response to the increase in magnitude of vertical velocities with resolution. This is essentially the hypothesis put forth by \cite{HR2017JCLIM} to explain resolution sensitivity, that increased vertical velocities with resolution interacts with other model components, steering the model towards a new mean state. Here, those interactions are documented in detail. Resolution sensitivity therefore arises from the relationship between vertical velocities and resolution, a well-known scale dependency of the equations of motion \citep{O1981JAS}. This scale dependency cannot be ignored in the pursuit of scale-aware physics.

>>>>

To isolate the relative importance of temperature or moisture on the systematic reduction in dilute CAPE with resolution for both ascending/descending regimes, dilute CAPE is recomputed for all resolutions, but through fixing the moisture profiles to the lowest resolution $ne20$ profile, and then through fixing only the temperature to the $ne20$ profile. Figure~\ref{fig:cape}d shows the influence of changing temperature profile with resolution on dilute CAPE of ascending/descending grid columns, and illustrates that the systematic reduction in dilute CAPE with resolution in both regimes is primarily from changes to the temperature field. Moisture changes with resolution do not contribute to the reduction in dilute CAPE with resolution, with the exception that the 20 J/kg reduction in dilute CAPE of ascending regions between the $ne80$ and $ne120$ runs (Figure~\ref{fig:cape}a) is entirely due to changes in moisture (not shown).

@@

This study argues that the sensitivity of parameterized convection and stratiform precipitation rates to resolution are a response to the increase in magnitude of vertical velocities with resolution. This is essentially the hypothesis put forth by \cite{HR2017JCLIM} to explain resolution sensitivity, that increased vertical velocities with resolution interacts with other model components, steering the model towards a new mean state. Here, those interactions are documented explicitly. Resolution sensitivity therefore arises from the relationship between vertical velocities and resolution, a well-known scale dependency of the equations of motion \citep{O1981JAS}. This scale dependency cannot be ignored in the pursuit of scale-aware physics.
